\documentclass[a4paper,11pt]{book}
%\documentclass[a4paper,twoside,11pt,titlepage]{book}
\usepackage{listings}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage{subfig}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{amsthm}
\usepackage{graphicx} % figuras
\usepackage{subfigure} % subfiguras

% \usepackage[style=list, number=none]{glossary} %
%\usepackage{titlesec}
%\usepackage{pailatino}

\decimalpoint
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{\esperiod}{-1}}
\makeatletter
\addto\shorthandsspanish{\let\esperiod\es@period@code}
\makeatother


%\usepackage[chapter]{algorithm}
\RequirePackage{verbatim}
%\RequirePackage[Glenn]{fncychap}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{afterpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{longtable}
\usepackage{minted}
\usepackage{bbding}

\usepackage{pgf,tikz}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}

\usepackage[pdfborder={000}]{hyperref} %referencia

% ********************************************************************
% Re-usable information
% ********************************************************************
\newcommand{\myTitle}{Voronoi-Diagrams \xspace}
\newcommand{\myDegree}{Doble Grado en Ingeniería Informática y Matemáticas \xspace}
\newcommand{\myName}{María Oliver Balsalobre \xspace}
\newcommand{\myProf}{Daniel Sánchez Fernández \xspace}
\newcommand{\myFaculty}{Facultad de Ciencias \xspace}
\newcommand{\myFacultyShort}{F. Ciencias \xspace}
\newcommand{\myDepartment}{Departamento de ... \xspace}
\newcommand{\myUni}{\protect{Universidad de Granada} \xspace}
\newcommand{\myLocation}{Granada \xspace}
\newcommand{\myTime}{\today \xspace}
\newcommand{\myVersion}{Version 0.1 \xspace}


\hypersetup{
pdfauthor = {\myName (mariaob (en) ugr (punto) es)},
pdftitle = {\myTitle},
pdfsubject = {},
pdfkeywords = {palabraclave1, palabraclave2, palabraclave3, ...},
pdfcreator = {LaTeX con el paquete ....},
pdfproducer = {pdflatex}
}

\hyphenation{}


%\usepackage{doxygen/doxygen}
%\usepackage{pdfpages}
\usepackage{url}
\usepackage{colortbl,longtable}
\usepackage[stable]{footmisc}
%\usepackage{index}

%\makeindex
%\usepackage[style=long, cols=2,border=plain,toc=true,number=none]{glossary}
% \makeglossary

% Definición de comandos que me son útiles:
%\renewcommand{\indexname}{Índice alfabético}
%\renewcommand{\glossaryname}{Glosario}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LO]{\leftmark}
\fancyhead[RE]{\rightmark}
\fancyhead[RO,LE]{\textbf{\thepage}}
\renewcommand{\chaptermark}[1]{\markboth{\textbf{#1}}{}}
\renewcommand{\sectionmark}[1]{\markright{\textbf{\thesection. #1}}}

\setlength{\headheight}{1.5\headheight}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
%Definimos los tipos teorema, ejemplo y definición podremos usar estos tipos
%simplemente poniendo \begin{teorema} \end{teorema} ...
\newtheorem{teorema}{Teorema}[chapter]
\newtheorem{proposicion}{Proposición}[chapter]
\newtheorem{corolario}{Corolario}[chapter]
\newtheorem{lema}{Lema}[chapter]
\newtheorem{ejemplo}{Ejemplo}[chapter]
\newtheorem{definicion}{Definición}[chapter]

\definecolor{gray97}{gray}{.97}
\definecolor{gray75}{gray}{.75}
\definecolor{gray45}{gray}{.45}
\definecolor{gray30}{gray}{.94}

\lstset{ frame=Ltb,
     framerule=0.5pt,
     aboveskip=0.5cm,
     framextopmargin=3pt,
     framexbottommargin=3pt,
     framexleftmargin=0.1cm,
     framesep=0pt,
     rulesep=.4pt,
     backgroundcolor=\color{gray97},
     rulesepcolor=\color{black},
     %
     stringstyle=\ttfamily,
     showstringspaces = false,
     basicstyle=\scriptsize\ttfamily,
     commentstyle=\color{gray45},
     keywordstyle=\bfseries,
     %
     numbers=left,
     numbersep=6pt,
     numberstyle=\tiny,
     numberfirstline = false,
     breaklines=true,
   }
 
% minimizar fragmentado de listados
%\lstnewenvironment{listing}[1][]
%   {\lstset{#1}\pagebreak[0]}{\pagebreak[0]}

\lstdefinestyle{CodigoC}
   {
	basicstyle=\scriptsize,
	frame=single,
	language=C,
	numbers=left
   }
\lstdefinestyle{CodigoC++}
   {
	basicstyle=\small,
	frame=single,
	backgroundcolor=\color{gray30},
	language=C++,
	numbers=left
   }

 
\lstdefinestyle{Consola}
   {basicstyle=\scriptsize\bf\ttfamily,
    backgroundcolor=\color{gray30},
    frame=single,
    numbers=none
   }


\newcommand{\bigrule}{\titlerule[0.5mm]}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
	backgroundcolor=\color{white},
	basicstyle=\footnotesize,
	breaklines=true,
	captionpos=b,
	commentstyle=\color{mygreen},
	escapeinside={\%*}{*)},
	keywordstyle=\color{blue},
	stringstyle=\color{mymauve},
	tabsize=2
}

%Para conseguir que en las páginas en blanco no ponga cabecerass
\makeatletter
\def\clearpage{%
  \ifvmode
    \ifnum \@dbltopnum =\m@ne
      \ifdim \pagetotal <\topskip
        \hbox{}
      \fi
    \fi
  \fi
  \newpage
  \thispagestyle{empty}
  \write\m@ne{}
  \vbox{}
  \penalty -\@Mi
}
\makeatother

\usepackage{pdfpages}
\raggedbottom
\begin{document}
\input{portada/portada}

\tableofcontents
\listoffigures
\renewcommand\listfigurename{\centering Índice de Figuras}

\input{prefacios/prefacio}

\input{capitulos/01_Introduccion}

\input{capitulos/02_Objetivos}

\input{capitulos/03_Desarrollo}

\input{capitulos/04_Conclusiones}

\begin{thebibliography}{1}
\addcontentsline{toc}{chapter}{Bibliografía}

\bibitem{clo} Franz Aurenhammer, Rolf Klein y Der-Tsai Lee, \emph{Voronoi Diagrams and delaunay Triangulations}, World Scientific, 2013.

\bibitem{qhull} Qhull, \emph{Voronoi Diagram}.  \url{http://www.qhull.org/html/qvoronoi.htm},  \url{http://www.qhull.org/html/qdelaun.htm}

\bibitem{java} Java™ Platform, Standard Edition 7
API Specification \url{https://docs.oracle.com/javase/7/docs/api/}.

\bibitem{java2} Programming Tutorials and Source Code Examples. \url{http://www.java2s.com/}

\bibitem{python} Python™. The Python Programming Language.
\url{https://www.python.org/}

\bibitem{pythonclass} SciPy: Fundamental Python library for scientific computing. Last updated on Mar 09, 2017.
\url{https://scipy.org/scipylib/index.html}

\bibitem{fotosfortune} Binay Bhattacharya. \emph{Notes from the book by de Berg, Van Krevald, Overmars, and Schwarzkpf. Fortune’s Algorithm}, 2011.
\url{http://www.cs.sfu.ca/~binay/813.2011/Fortune.pdf}

\bibitem{seidel} R. Seidel. \emph{Small-dimensional lineal programming and convex hulls made easy}. Discrete \& Computational Geometry 6, 1991.

\bibitem{yap} C.K. Yap. \emph{Fundamental Problems of Algorithmic Algebra}. Oxford University Press, 2000.

\bibitem{fotosincremental} Claudia Esteves Jaramillo, Johan Van Horebeek, Alonso Ramírez Manzanares. \emph{Curso de Análisis de Algoritmos}. Geometría Computacional, Diagramas de Voronoi. 2013. \url{http://www.cimat.mx/~alram/analisis_algo/07_DiagramasVoronoi.pdf}

\bibitem{fotosdividevenceras} Geometría Computacional. Ingeniería Informática e Ingeniería Técnica de Gestión. Diagramas de Voronoi, 2000-2001. \url{http://asignatura.us.es/fgcitig/contenidos/gctem3ma.htm}

\bibitem{gardenfor} Peter Gärdenfors. \emph{Conceptual Spaces. The Geometry of Thought}. MIT Press, 2004.

\bibitem{b-w} Bowyer-Watson algorithm, última edición en Marzo de 2017 \url{https://en.wikipedia.org/wiki/Bowyer%E2%80%93Watson_algorithm}

\bibitem{schspen} D.Schmitt and J.-C. Spehner. \emph{Angular properties of Delaunay diagrams in any dimensions.} Discrete \& Computational Geometry 5, 2000, 17-36.

\bibitem{mys} K. Mehlhorn and S. Näher. \emph{LEDA: A Platform for Combinatorial and Geometric Computing.} Cambridge University Press, 1999.

\bibitem{dewvran} A.K. Dewdney and J.K. Vranckh. \emph{A convex partition of $R^3$ with applications to Crum's problem and Knuth's post-office problem}. Utilitas Mathematica 12, 1977, 193-199.

\bibitem{joe} B. Joe. Geompack. \emph{A software package for the generation of meshes using geometric algorithms}. Advances in Engineering Software and Workstations 13, 1991, 325-331.

\bibitem{edersei} H. Edelsbrunner and R. Seidel. \emph{Voronoi Diagrams and arrangements.} Discrete \& Computational Geometry 1, 1986, 25-44.

\bibitem{aureimai} F. Autenhammer and H. Imai. \emph{Geometric relaions among Voronoi diagrams.} Geometriae Dedicata 27, 1988, 65-75.

\bibitem{alfortune} Dr. Eduardo A. Rodríguez Tello. CINVESTAV-Tamaulipas. 15 de marzo del 2013.
\url{http://www.tamps.cinvestav.mx/~ertello/gc/sesion16.pdf}

\bibitem {edelshah} H. Edelsbrunner and N.R. Shah. \emph{Incremental topological flipping works for regular triangulations}. Algorithmica, 1996.

\bibitem{voronoi} The Voronoi Web Site , última modificación en Junio de 2008. \url{http://www.voronoi.com}

\bibitem{circulos} François Anton, Darka Mioc, and Christopher Gold. \emph{The Voronoi diagram of circles and its application to the visualization of the growth of particles}, 2009. \url{http://www2.imm.dtu.dk/projects/graph/material/Anton_etal_2009.pdf}
\end{thebibliography}



%\bibliographystyle{miunsrturl}



%\thispagestyle{empty}

\end{document}
